### 2011-11-07 doc/pldi2012/experiments.tex

Figure~\ref{sfig:results2:perf} shows the throughput of the fluid benchmark when
run on various subsets of the CPUs and nodes in the cluster.  Performance is
normalized with respect to the serial execution case.  As in the circuit
simulation case, the same size problem is used for all runs, and we see 
speedups of up to 10.14x when using the entire cluster (a total of 48 CPUs).
The execution time breakdown in Table~\ref{sfig:results2:timers} shows some
differences in scaling behavior compared to the circuit simulation.  The time
spent performing copies is much smaller on absolute scale, but shows the same
large step when leaving a single node, but then relative insensitivity to the
number of nodes.  This indicates that the runtime is able to send data only to
the task that needs it rather than having to perform conservative broadcasts of
data to maintain consistency.

A more qualitative difference between the two simulations is that fluid shows
significant variability in the time spent in the application code, and there
are two separate issues at work.  First, the runtime is taking advantage of
the CPU's ability to perform RDMA operations to place some of the shared data
in the remotely-accessible memory windows provided by GASNet.  Although access
to this memory is significantly slower than accesses to a node's system memory,
being able to avoid copies entirely in some cases is a net win.

>>>>

Figure~\ref{sfig:results2:perf} shows the throughput of the fluid benchmark when
run on various subsets of the CPUs and nodes in the cluster.  Performance is
normalized with respect to the serial execution case.  As in the circuit
simulation case, the same size problem is used for all runs, and we see 
speedups of up to 10.14x when using the entire cluster (a total of 48 CPUs).
The execution time breakdown in Table~\ref{sfig:results2:timers} shows some
differences in scaling behavior compared to the circuit simulation.  The time
spent performing copies is much smaller on an absolute scale, but shows the same
large step when leaving a single node, but then relative insensitivity to the
number of nodes.  This indicates that the runtime is able to send data only to
the task that needs it rather than having to perform conservative broadcasts of
data to maintain consistency.

A more qualitative difference between the two simulations is that fluid shows
significant variability in the time spent in the application code, and there
are two separate issues at work.  First, the runtime is taking advantage of
the CPU's ability to perform RDMA operations to place some of the shared data
in the remotely-accessible memory windows provided by GASNet.  Although access
to this memory is slower than accesses to a node's system memory,
avoiding copies entirely in some cases is a net win.
